Report on the Fourth Working towards Sustainable Software for Science: Practice and Experiences (WSSSPE4) workshop

### 2016-09-14 WSSSPE4_report/WSSSPE4_report.tex
added section for survey response discussion
added files and mention of program committee
fixed Dan's affiliation

%
\thanks{{}$^{(1)}$ \hspace{-1ex}Computation Institute,
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu}
%

@@

@@

@@

>>>>

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu}
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Survey responses \label{sec:survey}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\todo{discuss survey responses}

@@

\todo{discuss Twitter activity}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Program committee}  \label{sec:progcom}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The following table lists the WSSSPE4 program committee.

{\scriptsize
\begin{longtable}{lll}
\input{program_committee}
\end{longtable}
}
